Playing with PCAs

### 2024-01-11 3-reports/playing_with_pcas.Rmd
PC1 loadings by transect and region

```{r, eval=FALSE}

@@

>>>>

```{r, eval=TRUE}

@@

PC1 loadings by transect
```{r}

pc_transect = 
  data_wide_PCA %>% 
  group_by(transect) %>% 
  do(get_pc_values(.)) %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc")))

pc_transect %>% 
  mutate(variable = fct_reorder(variable, abs(PC1))) %>% 
  ggplot(aes(x = abs(PC1), y = variable))+
  geom_point(size = 5)+
  scale_colour_manual(values = c("#81C0A7", "#1A421D"))+
 # xlim(0, 0.4)+
  #geom_vline(xintercept = 0)+
  labs(y = "",
       x = "|PC1|")+
  facet_grid(. ~ transect)+
  theme_kp()

PC1 loadings by region+transect
```{r}

pc_region_transect = 
  data_wide_PCA %>% 
  group_by(region, transect) %>% 
  do(get_pc_values(.)) %>% 
  mutate(transect = factor(transect, levels = c("upland", "transition", "wc")))

pc_region_transect %>% 
  mutate(variable = fct_reorder(variable, abs(PC1))) %>% 
  ggplot(aes(x = abs(PC1), y = variable, color = region))+
  geom_point(size = 5)+
  scale_colour_manual(values = c("#81C0A7", "#1A421D"))+
 # xlim(0, 0.4)+
  #geom_vline(xintercept = 0)+
  labs(y = "",
       x = "|PC1|")+
  facet_grid(. ~ transect)+
  theme_kp()
